XXXXX \todo{Le titre !} XXXXX

### 2013-03-22 parts/def-ph.tex
fix neighborhood
new restriction: boolean networks

While the construction of cooperation in PH allows to encode any boolean functions
between cooperating processes \cite{PMR10-TCSB}, it is worth noticing they introduce a temporal
shift in their application. \towrite{Adapter avec priorités}
This allows the existence of interleaving of actions leading to a cooperative sort representing a
past sub-state of the presence of the cooperative processes.
The resulting behavior is then an over-approximation
of the realization of an instantaneous cooperation.

@@

In this section, we describe several restrictions.
Although the definition of a Process Hitting with $k$ priorities allows a wide range of models, the method given in the next section only applies to Process Hitting models that regard these restrictions.

Let $\PH$ be a PH model on which we want to apply the static analysis.

We define the set of chains of actions $\PHh^n(b, a)$ between two sorts $b$ and $a$, with $n \in \segm{1}{k}$, as below:
\begin{align*}
\PHh^n(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\restriction{\PHh}{n})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_s)) = a \\
  & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
\end{align*}

We define the neighbor \towrite{Revoir terminologie : “neighborhood” ? “vicinity” ?} sorts of any sort $a$ and $n \in \segm{1}{k}$ as :
$$
\Vs^n(a) = \{ b \in \PHs \mid \PHh^m(b, a) \neq \emptyset \wedge m = \min(n, \prio(a)) \}
$$

@@

We define the neighbor actions of any sort $a$ as :
$$
\Vh(a) = \{ h \in \restriction{\PHh}{\prio(a)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}
$$

This PH has to regard the two following restrictions.

@@

\paragraph{Bounded reachability property}
The dynamics of model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
Formally : $\exists N \in \sN, \forall \delta \in \restriction{\Sce}{k-1}, |\indexes{\delta}| \leq N$.

@@

These restrictions bring new interesting properties to the PH models regarding them.

\pref{th:vplay} tells that for any action $h = \PHhit{a_i}{b_j}{b_k}$, if no action can be played in the neighborhood of $a$ in a given state, then $h$ can be played after a series of hits that do not prevent it to be fired. Furthermore, if the requisites of \pref{th:vplay} are true, then no action of this series of hits belongs to $V(a)$, as stated in \pref{co:vplay}.
\begin{theorem}
\label{th:vplay}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
  $\forall h' \in \Vh(a), \text{$h'$ cannot be played in $s$}) \Rightarrow (\exists \delta \in \Sce, \text{$h$ can be played in $s \PHplay \delta$})$
\end{theorem}

@@

\begin{corollary}
  \label{co:vplay}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
  $(\forall h' \in \Vh(a), \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
  $\exists \delta \in \Sce, (\forall n \in \indexes{\delta}, \delta_n \notin \Vh(a)) \wedge (\text{$h$ can be played in $s \PHplay \delta$})$
\end{corollary}

@@

\towrite{Théorème nécessaire pour la suite: une séquence d'actions dans $\BS(a)$ peut être jouée si précédée ou entrelacée par des $\zeta$ (?)}

>>>>

The construction of cooperation in PH allows to encode any boolean functions between cooperating processes \cite{PMR10-TCSB}.
Due to the presence of priorities, it is possible to build cooperations with no temporal shift by defining the actions on the cooperative sorts with the highest class of priority.
This allows to gain the same expressivity in PH than in boolean networks.
\towrite{Traduction BN depuis thèse.}

@@

%In this section, we describe several restrictions.
%Although the definition of a Process Hitting with $k$ priorities allows a wide range of models, the method given in the next section only applies to Process Hitting models that regard these restrictions.

\begin{comment}
We define the set of chains of actions $\PHh^n(b, a)$ between two sorts $b$ and $a$, with $n \in \segm{1}{k}$, as below:
\begin{align*}
\PHh^n(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\restriction{\PHh}{n})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_s)) = a \\
  & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
\end{align*}

We define the neighbor \towrite{Revoir terminologie : “neighborhood” ? “vicinity” ?} sorts of any sort $a$ and $n \in \segm{1}{k}$ as :
$$
\Vs^n(a) = \{ b \in \PHs \mid \PHh^m(b, a) \neq \emptyset \wedge m = \min(n, \prio(a)) \} \cup \{ a \}
$$

@@

We define the neighbor actions of any sort $a$ as :
$$
\Vh(a) = \{ h \in \restriction{\PHh}{\prio(a)} \mid \{ \PHsort(\PHhitter(h)), \PHsort(\PHtarget(h)) \} \subset \Vs(a) \wedge \prio(h) \leq \prio(a) \}
$$
\end{comment}

@@

Prédécesseurs prioritaires :
$$\Vs(a) = \{ b \in \PHs \mid \PHh^1(b, a) \neq \emptyset \}$$
$$\Vh(a) = \{ h \in \PHh^{(1)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}$$

Let $\PH$ be a PH model on which we want to apply the static analysis.
In this paper, we focus on a specific class of models that are equivalent to boolean networks.

\paragraph{Components \& cooperative sorts}
The studied PH is only composed of sorts representing regular components with priority $2$ and of cooperative sorts with priority $1$.

\begin{comment}
\paragraph{Bounded termination}
The dynamics of model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
Formally : $\exists N \in \sN, \forall \delta \in \restriction{\Sce}{k-1}, |\indexes{\delta}| \leq N$.

@@

\paragraph{Local stable states}
\towrite{Justification}
We define $\pfp$ as the set of possible stable states of a sort from a given state:
\begin{align*}
  \pfp_\ctx = \{ s \PHplay \delta \in \PHl &\mid s \in \ctx \wedge \delta \in \restriction{\Sce}{k-1} \\
  & \qquad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \restriction{\PHh}{k-1}, \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
  %\text{$h$ n'est pas jouable dans $s \PHplay \delta$} \}
\end{align*}

All processes are a stable state of a sub-state of the predecessors:
$\forall a_i \in \PHproc, \prio(a) < k \Rightarrow \exists s \in \restriction{\PHl}{\Vs(a)}, a_i \in \pfp_s$.
We note: $\stable_{a_i} = \{ s \in \restriction{\PHl}{\Vs(a)} \mid a_i \in \pfp_s \}$.
\end{comment}

\begin{comment}
These restrictions bring new interesting properties to the PH models regarding them.

\pref{th:vplay} tells that for any action $h = \PHhit{a_i}{b_j}{b_k}$, if no action can be played in the neighborhood of $a$ in a given state, then $h$ can be played after a series of hits that do not prevent it to be fired. Furthermore, if the requisites of \pref{th:vplay} are true, then no action of this series of hits belongs to $V(a)$, as stated in \pref{co:vplay}.
\begin{theorem}
\label{th:vplay}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
  $\forall h' \in \Vh^{\prio(b)-1}(a), \PHhitter(h') \notin s \wedge \PHtarget(h') \notin s) \Rightarrow$\\
  $(\exists \delta \in \Sce, \text{$h$ can be played in $s \PHplay \delta$})$
\end{theorem}

@@

\begin{corollary}
  \label{co:vplay}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
  $\forall h' \in \Vh^{\prio(b)-1}(a), \PHhitter(h') \notin s \wedge \PHtarget(h') \notin s) \Rightarrow$\\
  $\exists \delta \in \Sce, (\forall n \in \indexes{\delta}, \delta_n \notin \Vh(a)) \wedge (\text{$h$ can be played in $s \PHplay \delta$})$
\end{corollary}

@@

\towrite{Théorème nécessaire pour la suite: une séquence d'actions dans $\BS(a)$ peut être jouée si précédée ou entrelacée par des $\zeta$ (?)}
\end{comment}

### 2013-03-22 parts/sa.tex
new restriction: boolean networks

Processus rencontrés :
\begin{align*}
\allprocs((\cwSol,\cwReq,\cwCont,\cwSat)) = \{ p \in \PHproc &\mid \exists (P,ps) \in \cwSol, p \in ps
\\ & \vee p = \PHtarget(P)
%\\ & \vee (P \neq \omega \Rightarrow p = \PHbounce(P)) \}
\\ & \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \}
\end{align*}

\subsection{Local fixed points}

@@

\towrite{Formaliser}

Points fixes possibles : pour toute sorte $a$ et tout contexte $\ctx$:
\begin{align*}
  \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
  a &\mapsto \{ s \in \restriction{\PHl}{\Vs(a)} \mid \text{$s$ est (localement) accessible dans $\restriction{\PH}{\prio(a)}$ depuis $\ctx$}\\
  &\qquad\qquad\qquad\qquad \text{et aucune action n'y est jouable} \}
\end{align*}

Processus rencontrés comme résultats d'un point fixe :
\begin{align*}
\pfpprocs_\ctx(a) = \{ \PHget{s}{a} \mid s \in \pfp_\ctx(a) \}
\end{align*}

@@

\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
  $
  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}
  $,
  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \exists (Q, P) \in \myreq \cup \mysat \wedge ps \in \aBS(P) \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
    \\
    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_j \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
  \end{align*}
\end{definition}

@@

\begin{proof}
We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$ and
$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.

@@

  \item Suppose all children objectives of $P$ are concretizable.
  \begin{itemize}
    \item If $\exists Q \in \Bcont$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
      \begin{itemize}
%        \item[*] Let $\zeta_1 = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_1 \in \muconcr_s(\PHobj{\any}{b_i}), \PHget{s \PHplay \delta_1}{a} \in \pfp_s(a)$.
%          If $\PHget{s \PHplay \delta_1}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s \PHplay \delta_1}{a}}{a_k}) \in \Bsat$.
%          By hypothesis, $\muconcr_s(\PHobj{\any}{a_k}) \neq \emptyset$.
%          If $\PHget{s \PHplay \delta_1}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_1 \in \Sce$, $\zeta_1$ can be played in $s \PHplay \delta_1 \PHplay \delta'_1$.
        \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$, and we have: $\PHget{s_n \PHplay \delta_n}{a} \in \pfp_{s_n}(a)$.
          If $\PHget{s_n \PHplay \delta_n}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s_n \PHplay \delta_n}{a}}{a_k}) \in \Bsat$.
          By hypothesis, $\muconcr_{s_n \PHplay \delta_n}(\PHobj{\any}{a_k}) \neq \emptyset$.
          If $\PHget{s_n \PHplay \delta_n}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_n \in \Sce$, $\zeta_n$ can be played in $s \PHplay \delta_n \PHplay \delta'_n$
          \todo{Il reste à montrer que $\delta'_n$ ne perturbe pas $b$. Ça se montre par contradiction grâce à l'hyopthèse de cycle-freeness.}
          .
%        \item[*] For $n \in \segm{1}{m-1}$, $m = |\indexes{\zeta}|$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_n \PHplay \delta'_n \PHplay \zeta_n$ and $\zeta_{n+1} = \PHhit{c_i}{a_j}{a_k}$.
%          By hypothesis, $\exists \delta_1 \in \muconcr_{s_n}(\PHobj{\any}{c_i}), \PHget{s_n \PHplay \delta_{n+1}}{a} \in \pfp_s(a)$.
      \end{itemize}
      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
  \end{itemize}
\end{itemize}

Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (property \towrite{xxx}).
\end{proof}

>>>>

Processus rencontrés :
\begin{align*}
&\allprocs((\cwSol,\cwReq,\cwCont,\cwSat)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, p \in ps \\
  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
\end{align*}

\subsection{Local fixed points / possible bounces}

@@

\begin{comment}
Points fixes possibles : pour toute sorte $a$ et tout contexte $\ctx$:
\begin{align*}
  \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
  a &\mapsto \{ s \PHplay \delta \in \restriction{\PHl}{\Vs(a)} \mid s \in \restriction{\ctx}{\Vs(a)} \wedge \delta \in \restriction{\Sce}{\Vs(a)} \\
  &\qquad\qquad\qquad\qquad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
  %\text{$h$ n'est pas jouable dans $s \PHplay \delta$} \}
\end{align*}
%
Processus rencontrés comme résultats d'un point fixe :
\begin{align*}
\pfpprocs_\ctx(a) = \{ \PHget{s}{a} \mid s \in \pfp_\ctx(a) \}
\end{align*}
%
Le nouvel ensemble de processus à prendre en compte à chaque itération du pppf :
\begin{align*}
\newprocs_\ctx(\myB) = %\allprocs(\myB) \cup \bigcup_{a \in \PHs} \pfpprocs_{\allprocs(\myB)}(a)
  \{ a_k \in \PHproc &\mid a_k \in \allprocs(\myB) \vee \\
  & (a_i, \PHobjp{a}{j}{i}) \in \cwReq \wedge a_k \in \pfpprocs_{\ctx \Cap \allprocs(\myB)}(a) \wedge \\
  & \quad (\exists (P, ps) \in \cwSol, a_i \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
  & \quad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \cwSol, \exists p \in ps, \exists (p, P) \in \cwReq,\\
  & \qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
\end{align*}
\end{comment}

\begin{comment}
=================
%
Nouvelle version des états stables possibles: pour tout contexte $\ctx$:
\begin{align*}
  \pfp_\ctx = \{ s \PHplay \delta \in \PHl &\mid s \in \ctx \wedge \delta \in \restriction{\Sce}{k-1} \\
  & \qquad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \restriction{\PHh}{k-1}, \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
  %\text{$h$ n'est pas jouable dans $s \PHplay \delta$} \}
\end{align*}
%
Processus rencontrés comme résultats d'un état stable :
\begin{align*}
\pfpprocs_\ctx = \{ a_i \in \PHproc \mid \exists s \in \pfp_\ctx, a_i \in s \}
\end{align*}
%
Nouvel ensemble $\newprocs$ :
\begin{align*}
\newprocs_\ctx(\myB) = \allprocs(\myB) \cup \pfpprocs_\ctx
\end{align*}
\end{comment}

\begin{comment}
==========================

Bonds possibles :
\begin{align*}
\bounceprocs_\ctx = \{ a_i \in \PHproc \mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{k-1}, a_i \in (s \PHplay \delta) \}
\end{align*}
\end{comment}

États focaux possibles: pour tout contexte $\ctx \in \restriction{\PHl}{\Vs(a)}$:
\begin{align*}
  \pfp_\ctx(a) = \{ a_i \in \PHl_a &\mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{1}, \PHget{(\ctx \PHplay \delta)}{a} = a_i \\
  & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
\end{align*}

@@

\begin{definition}
  \label{def:aS}
  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
  $
  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}
  $,
  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
  \begin{align*}
    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
      a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
      & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
    \\
    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
    \\
    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
      \exists (P, ps) \in \mysol \\
      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
    \\
    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
      a_j \neq a_k \wedge a_k \in \pfp_\ctx(a) \}
%%% Version états stables locaux
%    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
%      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
%      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
%      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_i \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
%      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
%      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
  \end{align*}
\end{definition}

@@

\begin{proof}
\todo{À refaire}

\begin{comment}
We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$,
$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.

@@

  \item Suppose all children objectives of $P$ are concretizable.
  \begin{itemize}
    \item If $\exists Q \in \Bcont$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
%      \todo{Idée avec les nouvelles defs : au rang 0, on se replace sur un processus de $\pfp$. Au rang n, il existe par saturation un objectif adéquat qui “reprend” la progression.}
      \begin{itemize}
%        \item[*] Let $\zeta_1 = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_1 \in \muconcr_s(\PHobj{\any}{b_i}), \PHget{s \PHplay \delta_1}{a} \in \pfp_s(a)$.
%          If $\PHget{s \PHplay \delta_1}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s \PHplay \delta_1}{a}}{a_k}) \in \Bsat$.
%          By hypothesis, $\muconcr_s(\PHobj{\any}{a_k}) \neq \emptyset$.
%          If $\PHget{s \PHplay \delta_1}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_1 \in \Sce$, $\zeta_1$ can be played in $s \PHplay \delta_1 \PHplay \delta'_1$.
        \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$, and we have: $\PHget{s_n \PHplay \delta_n}{a} \in \bounceprocs_{s_n} \subset \bounceprocs_\ctx$ \todo{À montrer}.
          If $\PHget{s_n \PHplay \delta_n}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s_n \PHplay \delta_n}{a}}{a_k}) \in \Bsat$.
          By hypothesis, $\muconcr_{s_n \PHplay \delta_n}(\PHobj{\any}{a_k}) \neq \emptyset$.
          If $\PHget{s_n \PHplay \delta_n}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_n \in \restriction{\Sce}{k-1}$, $\zeta_n$ can be played in $s \PHplay \delta_n \PHplay \delta'_n$
          \todo{$\delta'_n$ ne perturbe pas $b$ ?}
          .
%        \item[*] For $n \in \segm{1}{m-1}$, $m = |\indexes{\zeta}|$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_n \PHplay \delta'_n \PHplay \zeta_n$ and $\zeta_{n+1} = \PHhit{c_i}{a_j}{a_k}$.
%          By hypothesis, $\exists \delta_1 \in \muconcr_{s_n}(\PHobj{\any}{c_i}), \PHget{s_n \PHplay \delta_{n+1}}{a} \in \pfp_s(a)$.
      \end{itemize}
      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
  \end{itemize}
\end{itemize}

Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (property \towrite{xxx}).
\end{comment}
\end{proof}
